\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, margin=1.0in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{tgpagella} 
%\usepackage{indentfirst}
\setlength\parindent{0pt}

\usepackage{xcolor}
\definecolor{dark-blue}{rgb}{0.15, 0.15, 0.4}

\usepackage{sectsty}
\sectionfont{\large\bf\uppercase}

\usepackage{titlesec}
\titlespacing*{\section}{0.0em}{0.2em}{0.0em}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}
\setlist[enumerate]{leftmargin=0.5in, itemsep=-0.5\parsep, topsep=-0.5\parskip}


\renewcommand{\baselinestretch}{1.04}
%\setlength{\parskip}{0.4em}
\newcommand\nl[1]{\item[] {#1}}
\newcommand\ml[1]{\item[--] {#1}}
\newcommand\pl[1]{\vspace{-0.2em}\begin{sloppypar}{#1}\end{sloppypar}}
\newcommand{\hr}{\hrule\vspace{0.5em}}


\begin{document}	

\begin{center}
	{\large \bf Jieyu Zhao}
\end{center}
\begin{center}
	{368 ENG VI, UCLA, CA | {https://jyzhao.net} | {jieyuzhao@ucla.edu}}
\end{center}

%----------------------------------------------------------------------------------------
%	Research Interests
%----------------------------------------------------------------------------------------
\section*{Research Interests}
\hr
\begin{itemize}
\item Detecting potential stereotypes in machine learning models
\item Developing computational approaches to enhance the fairness in NLP applications
\end{itemize}


%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section*{Education And Experience}
\hr
\textbf{Ph.D. University of California, Los Angele}, CA, USA \hfill {2017.09 - current}
	\begin{itemize}
	\item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
	\end{itemize}

\textbf{Ph.D. University of Virginia (withdrawal)}, VA, USA \hfill 2016.08 - 2017.08
	\begin{itemize}
	\item Major: Natural Language Processing, Machine Learning; Dept.~of Computer Science
	\end{itemize}

\textbf{M.S. Beihang University}, Beijing, China \hfill 2013.09 - 2016.01
	\begin{itemize}
	\item Major: Virtualization, Data Mining; School of Computer Science and Engineering
	\end{itemize}

\textbf{B.S. Beihang University}, Beijing, China \hfill 2009.09 - 2013.07
	\begin{itemize}
	\item Major: Computer Science and Engineering; School of Advanced Engineering
	\end{itemize}

\textbf{DiDi Chuxing} \hfill 2016.01 - 2016.05
	\begin{itemize}
	\item Intern, DiDi Chuxing Research, Beijing 
	\end{itemize}
\textbf{Microsoft} \hfill 2019.06 - 2019.09
	\begin{itemize}
	\item Intern, Microsoft Research, Redmond 
	\end{itemize}


%----------------------------------------------------------------------------------------
%	Research Interests and Patent
%----------------------------------------------------------------------------------------
\section*{Publications and Patent}
\hr
\hspace{0.32in}\textbf{Publications}
\begin{enumerate}
	\item T. Wang, \textbf{J. Zhao},  M. Yatskar, K. Chang, V. Ordonez. Balanced Datasets Are Not Enough: Estimating and Mitigating Gender Bias in Deep Image Representations. International Conference on Computer Vision (ICCV), 2019
	\item P. Zhou, W. Shi, \textbf{J. Zhao}, K.-H. Huang, M. Chen, K.-W. Chang. Examining Gender Bias in Languages with Grammatical Gender. Conference on Empirical Methods in Natural Language Processing \& International Joint Conference on Natural Language Processing (EMNLP-IJCNLP), 2019
	\item T. Sun, A. Gaut, S. Tang, Y. Huang, M. ElSherief, \textbf{J. Zhao}, M. Diba, B. Elizabeth, K.-W. Chang and W.Y. Wang. "Mitigating Gender Bias in Natural Language Processing: Literature Review. Association for Computational Linguistics (ACL), 2019
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, R. Cotterell , V. Ordonez, K.-W. Chang. Gender Bias in Contextualized Word Embeddings. North American Chapter of the Association for Computational Linguistics (NAACL), 2019
	\item \textbf{J. Zhao}, Y. Zhou, Z. Li, W. Wei, K.-W. Chang. Learning Gender Neutral Word Embeddings. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Gender Bias in Coreference Resolution: Evaluation and Debiasing Methods. North American Chapter of the Association for Computational Linguistics (NAACL), 2018
	\item \textbf{J. Zhao}, T. Wang, M. Yatskar, V. Ordonez, K.-W. Chang. Men Also Like Shopping: Reducing Gender Bias Amplification using Corpus-level Constraints. Conference on Empirical Methods in Natural Language Processing (EMNLP), 2017 {\color{red}\textbf{(Best Long Paper Award)}}
	\item \textbf{J. Zhao}, J. Li, B. Zhou, F. Chen, P. Tomchik, W. Ju. Parallel Algorithms for Anomalous Subgraph Detection. Concurrency and Computation: Practice and Experience, 29(3), e3769. 2017
	\item J. Li, \textbf{J. Zhao}, Y. Li, L. Cui, B. Li, L. Liu, J. Panneerselvam. iMIG: Toward an Adaptive Live Migration Method for KVM Virtual Machines. The Computer Journal, 58(6), 1227-1242. 2015
	\item B. Shi, B. Li, L. Cui, \textbf{J. Zhao}, J. Li. SyncSnap: Synchronized Live Memory Snapshots of Virtual Machine Networks. IEEE International Conference on High Performance Computing and Communications (HPCC), 2014
\end{enumerate}

\vspace{0.5em}
\hspace{0.32in}\textbf{Patent}
\begin{enumerate}
	\item 1.	B. Shi, B. Li, \textbf{J. Zhao}. An Algorithm for the Migration of ARM Virtual Machines. Patent Number: 83995027CN0. (submitted)
\end{enumerate}

%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------
\section*{Talks}
\hr
\begin{itemize}
\item Grace Hopper Celebration, September 2018
\item NLP highlights podcast, August 2018
\item Mid-Atlantic Student Colloquium on Speech, Language and Learning (MASC-SLL), May 2017
\end{itemize}

%----------------------------------------------------------------------------------------
%	Professional Activities
%----------------------------------------------------------------------------------------
\section*{Professional Activities}
\hr
Program Committee/Reviewer:
\begin{itemize}
\item AAAI 2019
\item Secondary reviewer EMNLP 2018
\item NLPCC-English 2018
\item NLPCC-Chinese 2018
\end{itemize}

%----------------------------------------------------------------------------------------
%	Teaching Experience
%----------------------------------------------------------------------------------------
\section*{Teaching Experience}
\hr
\textbf{UCLA}
\begin{itemize}
	\item Teaching Assistant, Introduction to Machine Learning, Kai-Wei Chang. 2019 Fall
\end{itemize}
\textbf{University of Virginia}
\begin{itemize}
\item Teaching Assistant, Algorithm, Kong-Cheng Wong. 2017 Spring
\item Teaching Assistant, Software Development Methods, Nada Basit and David Edwards. 2017 Spring
\item Teaching Assistant, Algorithm, Gabriel Robins. 2016 Fall
\item Teaching Assistant, Discrete Math, David Edwards. 2016 Fall
\end{itemize}

%----------------------------------------------------------------------------------------
%	Honors, Awards, and Scholarships
%----------------------------------------------------------------------------------------
\section*{Honors, Awards, and Scholarships}
\hr
\begin{enumerate}
\item SoCalNLP Symposium 2018 \textbf{Best Poster Award} \hfill 2018
\item UCLA \textbf{Graduate Division Fellowships} \hfill 2017
\item EMNLP 2017 \textbf{Best Long Paper Award} \hfill 2017
\item \textbf{Outstanding Graduate of Beijing City} \hfill 2016
\item Master Thesis Award \hfill 2016
\item 2nd Prize University Level Scholarship \hfill 2013, 2014, 2015
\item \textbf{Outstanding Graduate}, Beihang University. 6/236.	 \hfill 2014
\item \textbf{National Scholarship}. 2/236. \hfill 2014
\item The Award of ``\textbf{Outstanding Graduates}'' of Beihang University \hfill 2013
\item \textbf{Special Scholarship} for Freshmen. Top 6 of all freshmen (around 3000). \hfill 2009

\end{enumerate}



\end{document}

